\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-04-10 papers/methods/paper.tex
Separating out bulk plots for Bob

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{bulk_small2.pdf}
	\end{center}
	\caption{Posterior surfaces for 100 realisations of supernova data. Surfaces for $\Omega_m$, $w$, $\alpha$, $\beta$ and $\langle M_B \rangle$ are shown, with the other fit parameters being marginalised over. The intrinsic scatter model has significant impact on the recovered $\beta$, which in itself effects cosmology, resulting in small biases in $w$.}
	\label{fig:bulk_posterior}
\end{figure}

>>>>

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{bulk_small_g10.pdf}		\includegraphics[width=\columnwidth]{bulk_small_c11.pdf}
	\end{center}
	\caption{Posterior surfaces for 100 realisations of supernova data for two intrinsic dispersion models - the {\gten} model for the top panel and the {\celeven} model for the bottom panel. Surfaces for $\Omega_m$, $w$, $\alpha$, $\beta$ and $\langle M_B \rangle$ are shown, with the other fit parameters being marginalised over. The intrinsic scatter model has significant impact on the recovered $\beta$, which in itself effects cosmology, resulting in small biases in $w$.}
	\label{fig:bulk_posterior}
\end{figure}
